\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\usepackage{tocloft}
\usepackage{bm}
\usepackage{tcolorbox}
\usepackage{covington,tocloft}
\usepackage{graphics}
\usepackage{amsthm,amsmath}
\usepackage[font=small,compatibility=false]{caption}
\usepackage{amsfonts}
\usepackage{scrextend}
\usepackage{MnSymbol}%
\usepackage{wasysym}%
% \newtheorem{dummy}{Dummy}[section]
\newcounter{dummy} \numberwithin{dummy}{subsection}
\newtheorem{thm}[dummy]{Theorem}
\newtheorem{defn}[dummy]{Definition}
\newtheorem{prop}[dummy]{Proposition}
\newtheorem{lemma}[dummy]{Lemma}
\renewcommand{\qedsymbol}{\ensuremath{\blacksquare}}
\newcommand\myeq{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily def}}}{=}}}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}
\usepackage{float}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage[labelfont=bf]{caption}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}} 
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\floatstyle{plain}
\newfloat{example}{thp}{loc}
\floatname{example}{Example}
\def\bsq#1{%both single quotes
\lq{#1}\rq}
\usepackage{acronym}
\lstset{frame=tb,
  language=html,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\usepackage{subfiles}

\usepackage{blindtext}

\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\begin{document}


\subfile{chapters/chapter_0/title.tex}
\newpage

\tableofcontents
\newpage

%----------------------CHAPTER 1---------------------------------%
\section{Introduction}

\subfile{chapters/chapter_1/introduction.tex}
\newpage

%---------------------CHAPTER 2----------------------------------%
\section{Preliminaries}

%\subsection{Introduction}
\subfile{chapters/chapter_2/introduction.tex}

\subsection{Euclidean Inner Product}
\subfile{chapters/chapter_2/inner_product.tex}

\subsection{Integer Functions}
\subfile{chapters/chapter_2/integer_functions.tex}

\subsection{Computational Indistinguishability}
\subfile{chapters/chapter_2/comp_indist.tex}

\subsection{Leftover Hash Lemma}
\subfile{chapters/chapter_2/leftover_hash.tex}


%-------------------CHAPTER 3------------------------------------%
\section{Encryption}

%\subsection{Introduction}
\subfile{chapters/chapter_3/introduction.tex}

\subsection{Public Key Encryption}
\subfile{chapters/chapter_3/public_key_encryption.tex}

\subsection{Homomorphic Encryption}
\subfile{chapters/chapter_3/homomorphic_encryption.tex}

\subsubsection{Alice's Jewelry Store}
\subfile{chapters/chapter_3/jewelry_store.tex}

\subsubsection{Homomorphic Encryption}
\subfile{chapters/chapter_3/sub_homomorphic_encryption.tex}

\subsubsection{How to Construct a FHE Scheme}
\subfile{chapters/chapter_3/construct_fhe_scheme.tex}


%-------------------CHAPTER 4------------------------------------%
\section{Scale Invariant DGHV Scheme}

%\subsection{Introduction}
\subfile{chapters/chapter_4/introduction.tex}

\subsection{Constraints on the Parameters}
\subfile{chapters/chapter_4/param_constraints.tex}

\subsection{Public-Key Leveled Fully Homomorphic Encryption}
\subfile{chapters/chapter_4/pub_key_homomorphic_enc.tex}

\subsection{Proof of Correctness}
\subfile{chapters/chapter_4/proof_of_correctness.tex}

\subsubsection{Homomorphic Addition}
\subfile{chapters/chapter_4/homomorphic_add.tex}

\subsubsection{Homomorphic Multiplication}
\subfile{chapters/chapter_4/homomorphic_multip.tex}

\subsubsection{Convert Procedure}
\subfile{chapters/chapter_4/convert_proc.tex}

\subsubsection{Decrypt}
\subfile{chapters/chapter_4/decrypt.tex}

\subsection{Proof of Semantic Security}
\subfile{chapters/chapter_4/semantic_sec.tex}




%------------------REFERENCES----------------------------------%
\newpage
\thispagestyle{empty}
\section{References}
\bibliographystyle{plain}
\begin{thebibliography}{9}


\bibitem{latexcompanion} Rivest, R. L., Adleman, L. \& Dertouzos, M. L. (1978). On Data Banks and Privacy Homomorphisms. \textit{Foundations of Secure Computation}, Academia Press, 169-179. 

\bibitem{2} C. Gentry, \textit{A Fully Homomorphic Encryption Scheme}, Stanford University PhD thesis, 2009,
http://crypto.stanford.edu/craig/craig-thesis.pdf

\bibitem{3} Dasari, V., Palaparthy, A., \& Peddinti, K. (2014). \textit{Analysis of Different Fully Homomorphic Encryption Schemes}. Retrieved from http://ece.gmu.edu/coursewebpages/ECE/ECE646/F15/project/F15\allowbreak \_Project\_Resources/F14\_Homomorphic\_Encryption\_report.pdf

\bibitem{4} Shoup, V. \& Puniya, P. (2007). \textit{Advanced Cryptography: Lecture 8}. Lecture, https://cs.nyu.edu/courses/spring07/G22.3220-001/lec8.pdf.

\bibitem{5} Gentry, Craig. (2010) \textit{Computing arbitrary functions of encrypted data}. Communications of the ACM 53.3: 97-105.

\bibitem{6} Van Dijk, Marten, et al. (2010). \textit{Fully homomorphic encryption over the integers}. Advances in cryptology–EUROCRYPT 2010. Springer Berlin Heidelberg. 24-43.

\bibitem{7} Coron, Jean-Sébastien; Lepoint, Tancrède; Tibouchi, Mehdi (2014). \textit{Scale-Invariant Fully Homomorphic Encryption over the Integers}. PKC 2014. Springer.

\bibitem{8} CHEN, W. (1997). \textit{Linear Algebra} (pp. 1-16). Retrieved from https://rutherglen.science.mq.edu.au/wchen/lnlafolder/la09.pdf

\bibitem{9} Goldreich, O. (2003). \textit{Foundations of cryptography}. Cambridge, UK: Cambridge University Press.

\bibitem{10} Shelat, A. (2007). \textit{Indistinguishability and Pseudo-Randomness}. Retrieved from https://www.cs.virginia.edu/~shelat/651/www/chap3.pdf

\bibitem{11} Merca, M. (2011). Inequalities and Identities Involving Sums of Integer Functions. \textit{Journal Of Integer Sequences}. Retrieved from https://cs.uwaterloo.ca/journals/JIS/VOL14/Merca/merca3.html.

\bibitem{12} Saxena, N. (2009). \textit{Computational Security; Symmetric Key Encryption}. Lecture. Retrieved from http://isis.poly.edu/courses/cs6903-s09/Lectures/lecture3.pdf.

\end{thebibliography}
\newpage

\section{Appendix A: Bound Calculation}
\subfile{chapters/chapter_6_7/appendix_a.tex}

\section{Appendix B: Proof of Lemma 4.4.3}
\subfile{chapters/chapter_6_7/appendix_b.tex}

\end{document}